% !TeX root = 00-main.tex

\documentclass[00-main.tex]{subfiles}

\begin{document}

%\indexmarkstyle{\normalfont\tiny\sffamily}

%\showindexmarks


\pagestyle{empty}

\vfill

\begin{center}

	{\Huge\Children{New City Catechism}}

\end{center}

\vfill

\begin{center}
	Adapted By\\Timothy Keller And Sam Shammas\\From The\\Reformation Catechisms
\end{center}

\vfill

\begin{center}


	{\em Printed by and for the use of\\ St.\ John the Evangelist Anglican Church,\\ with permission}


\end{center}

\vfill

\begin{center}
\scriptsize\em Last revised: \today{}
\end{center}



\cleardoublepage

\pagestyle{plain}
\pagenumbering{roman}

\chapter*{New City Catechism}

\section*{Adapted By Timothy Keller And Sam Shammas From The Reformation Catechisms}

\begin{center}
\emph{Printed by and for the use of\\
St.\ John the Evangelist Anglican Church\\
PO Box 387\,\textbullet\,709 Easton Road\\
Willow Grove, PA, 19090-0387\\
215-396-1970\\
www.toknowchrist.org\\
info@toknowchrist.org}
\end{center}

Pursuant to the copyright, the details of which are in the following section, we:

\begin{itemize}
	\item {\em may}\/ use and share this material freely,
	\item {\em may not}\/ charge money for it, change the wording, or remove the copyright information.
\end{itemize}

Accordingly:

\begin{itemize}
\item Copies of this document are available for free from the church office at info@to\hspace{0em}know\hspace{0em}christ.\hspace{0em}org, or from our web site (www.to\hspace{0em}know\hspace{0em}christ.org).

\item You may purchase printed copies of this book from Lulu Press, Inc.\ printing services {\em at cost}. St.~John's makes no profit whatsoever from these purchases. The cost on the web site is exactly that which St.~John's must pay in order to obtain printed copies.

\item For economic reasons, there are two versions available, one with the children's answers in bolded text and one in color.\footnote{See page \pageref{whyversions} for further explanation about the children's answers.}
	\begin{itemize}
		\item \textbf{Black and white:} \href{http://www.lulu.com/content/paperback-book/new-city-catechism-b+bw/15095761}{www.lulu.com/content\slash{}paperback-book\slash{}new-city-catechism-b+bw\slash{}15095761}. At present, the price is \$2.16.
		
		\item \Children{Color:}\ \href{http://www.lulu.com/content/paperback-book/new-city-catechism-color/15320541}{www.lulu.com\slash{}content\slash{}paperback-book\slash{}new-city-\\catechism-color\slash{}15320541}. At present, the price is \$4.81.
	\end{itemize}
\end{itemize}

A fuller presentation of {\em New City Catechism\/} can be found outline at www.new\hspace{0em}city\hspace{0em}cat\hspace{0em}echism.\hspace{0em}com, with related texts of Scripture, a commentary from various authors, prayer, suggestions for further reading, a video explanation, and songs for kids related to each question. You can also find a link for a well-conceived and executed iPad application.


\cleardoublepage

\normalsize

\section*{{\em New City Catechism}\/ Copyright Notices}

\begin{itemize}
	\item Devised and adapted by Timothy Keller and Sam Shammas from the Reformation catechisms, produced by Ben Peays.
	\item Copyright {\textcopyright} 2012 by Redeemer Presbyterian Church.
	\item We encourage you to use and share this material freely\thinspace{}---\thinspace{}but please don't charge money for it, change the wording, or remove the copyright information.
	\item NIV Scripture quotations are taken from The Holy Bible, New International Version,\textsuperscript{{\textregistered}} NIV\textsuperscript{{\textregistered}}. Copyright {\textcopyright} 1973, 1978, 1984, 2011 by Biblica, Inc.{\texttrademark} Used by permission. All rights reserved worldwide.
	\item ESV Scripture quotations are from The Holy Bible, English Standard Version\textsuperscript{{\textregistered}} (ESV\textsuperscript{{\textregistered}}), copyright {\textcopyright} 2001 by Crossway, a publishing ministry of Good News Publishers. Used by permission. All rights reserved.
	\item {\sloppy Videos produced by The Gospel Coalition and Redeemer Presbyterian Church. Directed by Sam Shammas. Filmed by Scott Smith. Edited by Peter Ostebo.}
	\item App by Brushfire.
	\item The Gospel Coalition and Redeemer Presbyterian Church would like to thank all those who trialled, reviewed, and participated in the filming of {\em New City Catechism}.
	\item All songs provided by Songs for Saplings, Portland, OR. Songs are from the Questions with Answers series by Dana Dirksen, based on the Westminster Shorter Catechism, 1647. More information is available at \href{songsforsaplings.com}{songs\hspace{0em}for\hspace{0em}sap\hspace{0em}lings.\hspace{0em}com}.
\end{itemize}

\clearpage

\vfill

\small

\begin{center}

\noindent\emph{This document was typeset using {\em\LaTeX\/},\\ a high-quality typesetting system\\  developed by Leslie Lamport as a superset of\\ Donald Knuth's {\em\TeX\/} typesetting program.}

\bigskip

\emph{The font used is Linux Libertine,\\ a public domain font from the Libertine font family\\ developed by the {\em Libertine Open Fonts Projekt}.}

\bigskip

\emph{For more information, see:\\ 
\href{latex-project.org}{latex-project.org},\\
\href{tug.org}{tug.org}, and,\\ \href{www.linuxlibertine.org}{www.\hspace{0em}linuxlibertine.\hspace{0em}org}.}

\end{center}
\normalsize

\vfill

\cleardoublepage

\tableofcontents

\cleardoublepage


\end{document}
