\documentclass[00-main.tex]{subfiles}

\begin{document}

\section{Q 3. How many persons are there in God?}

\Children{There are three persons in }the \Children{one }true and living \Children{God: the Father, the Son, and the Holy Spirit.} They are the same in substance, equal in power and glory.

\Quote{2 Corinthians 13:14\index[1co]{13:14}}{May the grace of the Lord Jesus Christ, and the love of God, and the fellowship of the Holy Spirit be with you all.}

\subsection{Commentary}

``The \dots Trinity, Father, Son, and Holy Ghost, being one God, is \dots ne\-ces\-sa\-ry to us to be believed, not only as to the eternal \dots but especially for the knowledge of God's three great sorts of works on man: that is, as our Creator, and the God of nature; as our Redeemer, and the God of governing and reconciling grace, and as our Sanctifier, and the Applier and Perfecter of all to fit us to glory.

The Scripture tells us that there are three, and yet but one God. \dots  We are to be baptised into the name of the Father, Son, and Holy Ghost (Matt. xxviii. 29.)\index[mat]{28:29} And there are three that bear record in heaven, the Father, the Word, and the Holy Spirit, and these three are one (1 John v. 7.)\index[1jo]{5:07@5:7} \dots  [That] God is one infinite, undivided Spirit; and yet that he is Father, Son, and Holy Ghost, must be believed.

We must \dots know, believe and esteem him to be the only infinite, eternal, self-sufficient Spirit, vital Power, Understanding, and Will, our most perfect Life, Light, and Love; Father, Son, and Holy Ghost, of whom, and through whom, and to whom, are all things; our absolute Owner, Ruler, and Father; our Maker, our Redeemer, and Sanctifier.''

\begin{NameCite}
{Richard}{Baxter}{Baxter:1830}{pp.\ 33, 62, 165}
Richard Baxter\index[people]{Baxter, Richard}\label{baxter:q3}
\end{NameCite}

\subsection{Prayer}
``Not without trembling, we have entreated of the most holy mystery of the reverend Trinity, the Father, the Son, and the Holy Ghost, which we have learned out of the scriptures: and here now we will stay, humbly worshipping this Unity in trinity and Trinity in unity. And let us keep in mind and acknowledge this distinction or division most manifestly declared in the scriptures, and the unity also commended unto us with exceeding great diligence \dots. There is but one God \dots. Therefore when we read that God created the world, we understand that the Father from whom are all things, by the Son by whom are all things, in the Holy Ghost in whom are all things, created the world. And when we read that the Son became flesh, suffered, died, and rose again for our salvation, we believe that the Father and the Holy Ghost, though they were not partakers of his incarnation and passion, yet notwithstanding that they wrought our salvation by the Son \dots. And when sins are said to be forgiven in the Holy Ghost, we believe that this benefit and all other benefits of our blessedness are unseparably given and bestowed upon us from one, only, true, living, and everlasting God, who is the Father, the Son, and the Holy Ghost. To whom be praise and thanksgiving for ever and ever. Amen.''

\begin{NameCite}
{Henry}{Bullinger}{Bullinger:1851}{pp.\ 325--326}
\end{NameCite}

\begin{multicols*}{2}
	\subsection{Further Reading}
	
	``Trinity'' in \cite{Packer:2001}.\index[people]{Packer, J.I.}
	
	\subsection{Video}
	\href{https://vimeo.com/46824536}{vimeo.com\slash{}46824536}
\end{multicols*}

\end{document}