\documentclass[00-main.tex]{subfiles}

\begin{document}

\section{Q 2. What Is God?}

\Children{God is the creator }and sustainer \Children{of everyone and everything.} He is eternal, infinite, and unchangeable in his power and perfection, goodness and glory, wisdom, justice, and truth. Nothing happens except through him and by his will.

\Quote{Psalm 86:8--10\index[psa]{86:8--10} and 15\index[psa]{86:15}}{Among the gods there is none like you, Lord; no deeds can compare with yours. All the nations you have made will come and worship before you, Lord; they will bring glory to your name. For you are great and do marvelous deeds; you alone are God \dots You, Lord, are a compassionate and gracious God, slow to anger, abounding in love and faithfulness.}

\subsection{Commentary}

``God is an eternal, independent being \dots. He gives being to all creatures \dots. God is an eternal, unchangeable being \dots. His being is without any limits. Angels and men have their beings, but then they are bounded and limited; \dots but God is an immense being that cannot be included within any bounds \dots. There never was nor shall be time wherein God could not say of himself, `I am' \dots. He is a God that gives being to all things \dots. He is the Being of beings, subsisting by himself; \dots `I am that I am, and as I am, so will I be to all eternity' \dots. He is infinite in power, sovereign in dominion, and not bounded as creatures are \dots. He is so strong that he is almighty, he is one to whom nothing is impossible \dots. He wanteth nothing, but is infinitely blessed with the infinite perfection of his glorious being \dots self-sufficient, all-sufficient, absolutely perfect \dots. There is no succession or variation in God, but he is eternally the same \dots. God ever was, ever is, and ever shall be. Though the manifestations of himself unto the creatures are in time, yet his essence or being never did nor shall be bound up by time. Look backward or forward, God from eternity to eternity, is a most self-sufficient, infinite, perfect, blessed being, the first cause of our being, and without any cause of his own being; an eternal infinite fulness, and possession to himself and of himself. What God is, he was from eternity, and what God is, he will be so to eternity.''

\begin{NameCite}
{Thomas}{Brooks}{Brooks:1866a}{150--157}
\end{NameCite}

\subsection{Prayer}
``I believe, O sovereign Goodness, O mighty Wisdom, that thou dost sweetly order and govern all things, even the most minute, even the most noxious, to thy glory, and the good of those that love thee. I believe, O Father of the families of heaven and earth, that thou so disposest all events, as may best magnify thy goodness to all thy children, especially those whose eyes wait upon thee. I most humbly beseech thee, teach me to adore all thy ways, though I cannot comprehend them; teach me to be glad that thou art king, and to give thee thanks for all things that befall me; seeing thou hast chosen that for me, and hast thereby `set to thy seal that they are good'. And for that which is to come, give me thy grace to do in all things what pleaseth thee; and then, with an absolute submission to thy wisdom, to leave the issues of them in thy hand.''

\begin{NameCite}
{John}{Wesley}{Wesley:1831}{392}
\end{NameCite}

\begin{multicols*}{2}
\subsection{Biographies}

\begin{itemize}
	\item For Thomas Brooks, see page \pageref{brooks}.
	\item For John Wesley, see page \pageref{wesley}.
\end{itemize}

\subsection{Further Reading}
\flushleft{``Self-existence'', ``Transcendence'', and ``Almightiness'' in \cite{Packer:2001}.\index[people]{Packer, J.I.}}

\subsection{Video}
\href{https://vimeo.com/46824534}{vimeo.com\slash{}46824534}
\end{multicols*}

\end{document}