\documentclass[00-main.tex]{subfiles}

\begin{document}

\section{Q  1. What is our only hope in life and death?}
\Children{That we are not our own but belong, body and soul, both in life and death, to God and to our Savior Jesus Christ.}

\Quote{Romans 14:7--8\index[rom]{14:7--8}}{For none of us lives to himself, and none of us dies to himself. For if we live, we live to the Lord, and if we die, we die to the Lord. So then, whether we live or whether we die, we are the Lord's.}

\subsection{Commentary}
``If we, then, are not our own but the Lord's, it is clear what error we must flee, and whither we must direct all the acts of our life. We are not our own: let not our reason nor our will, therefore, sway our plans and deeds. We are not our own: let us therefore not set it as our goal to seek what is expedient for us \dots. We are not our own: in so far as we can, let us forget ourselves and all that is ours. Conversely, we are God's: let us therefore live for him and die for him. We are God's: let his wisdom and will therefore rule all our actions. We are God's: let all the parts of our life accordingly strive toward him as our only lawful goal. O, how much has that man profited who, having been taught that he is not his own, has taken away dominion and rule from his own reason that he may yield it to God! For, as consulting our self-interest is the pestilence that most effectively leads to our destruction, so the sole haven of salvation is to be wise in nothing and to will nothing through ourselves but to follow the leading of the Lord alone.''
\begin{NameCite}
	{John}{Calvin}{Calvin:1960}{III. VII. I., 690}
\end{NameCite}

\subsection{Prayer}
``Lord, here am I; do with me what thou pleasest, write upon me as thou pleasest: I give up myself to be at thy dispose \dots. The ambitious man giveth himself up to his honours, but I give up myself unto thee; \dots\ man gives himself up to his pleasures, but I give up myself to thee; \dots\ man gives himself up \dots\ to his idols, but I give myself to thee \dots\. Lord! lay what burden thou wilt upon me, only let thy everlasting arms be under me \dots. I am lain down in thy will, I have learned to say amen to thy amen; thou hast a greater interest in me than I have in myself, and therefore I give up myself unto thee, and am willing to be at thy dispose, and am ready to receive what impression thou shalt stamp upon me. O blessed Lord! hast thou not again and again said unto me \dots\ `I am thine, O soul! to save thee; my mercy is thine to pardon thee; my blood is thine to cleanse thee; my merits are thine to justify thee; my righteousness is thine to clothe thee; my Spirit is thine to lead thee; my grace is thine to enrich thee; and my glory is thine to reward thee'; and therefore \dots\ I cannot but make a resignation of myself unto thee. Lord! here I am, do with me as seemeth good in thine own eyes. I know the best way \dots\ is to resign up myself to thy will, and to say amen to thy amen.

\begin{NameCite}{Thomas}{Brooks}{Brooks:1866}{305--306}\end{NameCite}

\begin{multicols*}{2}
\subsection{Biographies}

\begin{itemize}
	\item For Thomas Brooks, see page \pageref{brooks}.
	\item For John Calvin, see page \pageref{calvin}.
\end{itemize}

	\subsection{Further Reading}
	``Salvation'' in \cite{Packer:2001}.\index[people]{Packer, J.I.}

	\subsection{Video}
	\href{https://vimeo.com/46824533}{vimeo.com\slash{}46824533}
\end{multicols*}

\end{document}