\documentclass[00-main.tex]{subfiles}

\begin{document}

%\indexmarkstyle{\normalfont\tiny\sffamily}

%\showindexmarks


\pagestyle{empty}

\vfill

\begin{center}
	\begin{minipage}{2.9in}
	{\centering
	\Huge{New City Catechism}
	\par}
	\end{minipage}
\end{center}

\vfill

\begin{center}
	\begin{minipage}{2.9in}
	{\centering
	Adapted By\\
	Timothy Keller And Sam Shammas\\
	From The\\
	Reformation Catechisms.\par}
	\end{minipage}
\end{center}

\vfill

\begin{center}
	\begin{minipage}{2.9in}
	\begin{center}
	{\em Printed by and for the use of\\ St.\ John the Evangelist Anglican Church,\\ with permission.}
	\end{center}
	\end{minipage}
\end{center}

\vfill

\cleardoublepage

\pagestyle{plain}
\pagenumbering{roman}

\chapter*{New City Catechism}

\section*{Adapted By Timothy Keller And Sam Shammas From The Reformation Catechisms.}

Printed by and for the use of St.\ John the Evangelist Anglican Church.

\vspace{-1em}

\begin{center}
\emph{PO Box 387\,\textbullet\,709 Easton Road\\
Willow Grove, PA, 19090-0387\\
215-396-1970\\
www.toknowchrist.org\\
info@toknowchrist.org}
\end{center}

Pursuant to the copyright (details of which are on the following page), we:

\begin{itemize}
	\item {\em may}\/ use and share this material freely,
	\item {\em may not}\/ charge money for it, change the wording, or remove the copyright information.
\end{itemize}

Accordingly:

\begin{itemize}
	\item Copies of this document are available for free from the church office at info@to\hspace{0em}know\hspace{0em}christ.\hspace{0em}org, our web site (http:\slash{}\slash{}www.to\hspace{0em}know\hspace{0em}christ.org), or from http:\slash{}\slash{}www.new\hspace{0em}city\hspace{0em}cate\hspace{0em}chism.\hspace{0em}com.
	\item It is our plan to provide printed copies from Lulu Press, Inc. printing services (www.lulu.com) at cost. When that plan comes to fruition, St.\ John's will make no profit whatsoever: the cost on the web site will be exactly that which St.\ John's must pay in order to obtain printed copies.
\end{itemize}

A fuller presentation of {\em New City Catechism}\/ can be found outline at http:\slash{}\slash{}www.new\hspace{0em}city\hspace{0em}cat\hspace{0em}echism.\hspace{0em}com, with related texts of Scripture, a commentary from various authors, prayer, suggestions for further reading, a video explanation, and songs for kids related to each question. You can also find a link for an excellently conceived and executed iPad application.

\cleardoublepage

\section*{{\em New City Catechism}\/ Copyright Notices}

\begin{itemize}
	\item Devised and adapted by Timothy Keller and Sam Shammas from the Reformation catechisms, produced by Ben Peays.
	\item Copyright {\textcopyright} 2012 by Redeemer Presbyterian Church.
	\item We encourage you to use and share this material freely\thinspace{}---\thinspace{}but please don't charge money for it, change the wording, or remove the copyright information.
	\item NIV Scripture quotations are taken from The Holy Bible, New International Version,\textsuperscript{{\textregistered}} NIV\textsuperscript{{\textregistered}}. Copyright {\textcopyright} 1973, 1978, 1984, 2011 by Biblica, Inc.{\texttrademark} Used by permission. All rights reserved worldwide.
	\item ESV Scripture quotations are from The Holy Bible, English Standard Version\textsuperscript{{\textregistered}} (ESV\textsuperscript{{\textregistered}}), copyright {\textcopyright} 2001 by Crossway, a publishing ministry of Good News Publishers. Used by permission. All rights reserved.
	\item {\sloppy Videos produced by The Gospel Coalition and Redeemer Presbyterian Church. Directed by Sam Shammas. Filmed by Scott Smith. Edited by Peter Ostebo.}
	\item App by Brushfire.
	\item The Gospel Coalition and Redeemer Presbyterian Church would like to thank all those who trialled, reviewed, and participated in the filming of {\em New City Catechism}.
	\item All songs provided by Songs for Saplings, Portland, OR. Songs are from the Questions with Answers series by Dana Dirksen, based on the Westminster Shorter Catechism, 1647. More info at http:\slash{}\slash{}songs\hspace{0em}for\hspace{0em}sap\hspace{0em}lings.com.
\end{itemize}

\cleardoublepage

\setcounter{tocdepth}{2}

\tableofcontents

\cleardoublepage


\end{document}
