\documentclass[00-main.tex]{subfiles}

\begin{document}


\section{Part 1. God, Creation And Fall, Law}

\subsection{Q  1. What is our only hope in life and death?}
\Children{That we are not our own but belong, body and soul, both in life and death, to God and to our Savior Jesus Christ.}

\Quote{Romans 14:7--8\index[rom]{14:7--8}}{For none of us lives for ourselves alone, and none of us dies for ourselves alone. If we live, we live for the Lord; and if we die, we die for the Lord. So, whether we live or die, we belong to the Lord.}

\subsubsection{Commentary}

\label{q1comment}``If we, then, are not our own but the Lord's, it is clear what error we must flee, and whither we must direct all the acts of our life. We are not our own: let not our reason nor our will, therefore, sway our plans and deeds. We are not our own: let us therefore not set it as our goal to seek what is expedient for us  \dots{}. We are not our own: in so far as we can, let us forget ourselves and all that is ours. Conversely, we are God's: let us therefore live for him and die for him. We are God's: let his wisdom and will therefore rule all our actions. We are God's: let all the parts of our life accordingly strive toward him as our only lawful goal. O, how much has that man profited who, having been taught that he is not his own, has taken away dominion and rule from his own reason that he may yield it to God! For, as consulting our self-interest is the pestilence that most effectively leads to our destruction, so the sole haven of salvation is to be wise in nothing and to will nothing through ourselves but to follow the leading of the Lord alone.''\footnote{From John Calvin's\index[people]{Calvin, John} \index[book]{Institutes Of The Christian Religion}{\em Institutes of the Christian Religion}, edited by John T.\ McNeill, translated by Ford Lewis Battles, Library of Christian Classics (Philadelphia: Westminster, 1960), III.VII.I., 690.}

\subsubsection{Further Reading}

``Salvation'' in \index[book]{Concise Theology}{\em Concise Theology}, by \index[people]{J.\ I.\ Packer}J.\ I.\ Packer.

\subsubsection{Prayer}

\label{q1prayer}``Lord, here am I; do with me what thou pleasest, write upon me as thou pleasest: I give up myself to be at thy dispose \dots{} The ambitious man giveth himself up to his honours, but I give up myself unto thee; \dots{} man gives himself up to his pleasures, but I give up myself to thee; \dots{} man gives himself up \dots{} to his idols, but I give myself to thee \dots. Lord! lay what burden thou wilt upon me, only let thy everlasting arms be under me \dots. I am lain down in thy will, I have learned to say amen to thy amen; thou hast a greater interest in me than I have in myself, and therefore I give up myself unto thee, and am willing to be at thy dispose, and am ready to receive what impression thou shalt stamp upon me. O blessed Lord! hast thou not again and again said unto me \dots{} `I am thine, O soul! to save thee; my mercy is thine to pardon thee; my blood is thine to cleanse thee; my merits are thine to justify thee; my righteousness is thine to clothe thee; my Spirit is thine to lead thee; my grace is thine to enrich thee; and my glory is thine to reward thee’; and therefore \dots{} I cannot but make a resignation of myself unto thee. Lord! here I am, do with me as seemeth good in thine own eyes. I know the best way \dots{} is to resign up myself to thy will, and to say amen to thy amen.''\footnote{From \index[book]{The Mute Christian Under the Smarting Rod}``The Mute Christian Under the Smarting Rod'' in {\em The Complete Works of Thomas Brooks}\index[people]{Brooks, Thomas}, edited by Rev.\ Alexander Balloch Grosart, Volume 1 (Edinburgh: James Nichol, 1866), 305--306.}







\subsection{Q  2. What Is God?}
\Children{God is the creator }and sustainer \Children{of everyone and everything.} He is eternal, infinite, and unchangeable in his power and perfection, goodness and glory, wisdom, justice, and truth. Nothing happens except through him and by his will.

\Quote{Psalm 86:8--10\index[psa]{86:8--10} and 15\index[psa]{86:15}}{Among the gods there is none like you, Lord; no deeds can compare with yours. All the nations you have made will come and worship before you, Lord; they will bring glory to your name. For you are great and do marvelous deeds; you alone are God\,\dots\,You, Lord, are a compassionate and gracious God, slow to anger, abounding in love and faithfulness.}


\subsection{Q  3. How many persons are there in God?}
\Children{There are three persons in }the \Children{one }true and living \Children{God: the Father, the Son, and the Holy Spirit.} They are the same in substance, equal in power and glory.

\Quote{2 Corinthians 13:14\index[1co]{13:14}}{May the grace of the Lord Jesus Christ, and the love of God, and the fellowship of the Holy Spirit be with you all.}


\subsection{Q  4. How and why did God create us?}
\Children{God created us male and female in his own image to }know him, love him, live with him, and \Children{glorify him.} And it is right that we who were created by God should live to his glory.

\Quote{Genesis 1:27\index[gen]{1:27}}{So God created mankind in his own image, in the image of God he created them; male and female he created them.}


\subsection{Q  5. What else did God create?}
\Children{God created all things }by his powerful Word, \Children{and all his creation was very good}; everything flourished under his loving rule\Children{.}

\Quote{Genesis 1:31\index[gen]{1:31}}{God saw all that he had made, and it was very good.}


\subsection{Q  6. How can we glorify God?}
We glorify God \Children{by }enjoying him, \Children{loving him}, trusting him, \Children{ and by obeying his }will, \Children{commands, and law.}

\Quote{Deuteronomy 11:1\index[deu]{11:1}}{Love the \textsc{Lord} your God and keep his requirements, his decrees, his laws and his commands always.}


\subsection{Q 7. What does the law of God require?}
Personal, perfect, and perpetual obedience; \Children{that we love God with all our heart, soul, mind, and strength; and love our neighbor as ourselves.} What God forbids should never be done and what God commands should always be done.

\Quote{Matthew 22:37--40\index[mat]{22:37--40}}{Jesus replied: ``Love the Lord your God with all your heart and with all your soul and with all your mind. This is the first and greatest commandment. And the second is like it: Love your neighbor as yourself. All the Law and the Prophets hang on these two commandments.''}

\subsection{Q 8. What is the law of God stated in the Ten Commandments?}
\Children{You shall have no other gods before me. You shall not make for yourself an idol} in the form of anything in heaven above or on the earth beneath or in the waters below\thinspace{}---\thinspace{}you shall not bow down to them or worship them\Children{. You shall not misuse the name of the \textsc{Lord} your God. Remember the Sabbath day by keeping it holy. Honor your father and your mother. You shall not murder. You shall not commit adultery. You shall not steal. You shall not give false testimony. You shall not covet.}

\Quote{Exodus 20:3\index[exo]{20:3} and Deuteronomy 5:7\index[deu]{05:7@5:7}}{You shall have no other gods before me.}

\subsection{Q 9. What does God require in the first, second, and third commandments?}
\Children{First, that we know }and trust \Children{God as the only true }and living \Children{God. Second, that we avoid all idolatry }and do not worship God improperly\Children{. Third, that we treat God's name with fear and reverence}, honoring also his Word and works\Children{.}

\Quote{Deuteronomy 6:13--14\index[deu]{06:13--14@6:13--14}}{Fear the \textsc{Lord} your God, serve him only and take your oaths in his name. Do not follow other gods, the gods of the peoples around you.}

\subsection{Q 10. What does God require in the fourth and fifth commandments?}
\Children{Fourth, that on the Sabbath day we spend time in }public and private \Children{worship of God}, rest from routine employment, serve the Lord and others, and so anticipate the eternal Sabbath\Children{. Fifth, that we love and honor our father and our mother}, submitting to their godly discipline and direction\Children{.}

\Quote{Leviticus 19:3\index[lev]{19:3}}{Each of you must respect your mother and father, and you must observe my Sabbaths. I am the \textsc{Lord} your God.}

\subsection{Q 11. What does God require in the sixth, seventh, and eighth commandments?}
\Children{Sixth, that we do not hurt, or hate}, or be hostile to \Children{ our neighbor}, but be patient and peaceful, pursuing even our enemies with love\Children{. Seventh, that we }abstain from sexual immorality and \Children{live purely and faithfully}, whether in marriage or in single life, avoiding all impure actions, looks, words, thoughts, or desires, and whatever might lead to them\Children{. Eighth, that we do not take without permission that which belongs to someone else}, nor withhold any good from someone we might benefit\Children{.}

\Quote{Romans 13:9\index[rom]{13:9}}{The commandments, ``You shall not commit adultery,'' ``You shall not murder,'' ``You shall not steal,'' ``You shall not covet,'' and whatever other command there may be, are summed up in this one command: ``Love your neighbor as yourself.''}

\subsection{Q 12. What does God require in the ninth and tenth commandments?}
\Children{Ninth, that we do not lie or deceive}, but speak the truth in love\Children{. Tenth, that we are content, not envying anyone} or resenting what God has given them or us\Children{.}

\Quote{James 2:8\index[jam]{2:8}}{If you really keep the royal law found in Scripture, ``Love your neighbor as yourself,'' you are doing right.}

\subsection{Q 13. Can anyone keep the law of God perfectly?}
\Children{Since the fall, no }mere \Children{human has been able to keep the law of God perfectly}, but consistently breaks it in thought, word, and deed\Children{.}

\Quote{Romans 3:10--12\index[rom]{03:10--12@3:10--12}}{There is no one righteous, not even one; there is no one who understands; there is no one who seeks God. All have turned away, they have together become worthless; there is no one who does good, not even one.}

\subsection{Q 14. Did God create us unable to keep his law?}
\Children{No, but because of the disobedience of }our first parents, \Children{Adam and Eve}, all of creation is fallen\Children{; we are all born in sin and guilt,} corrupt in our nature and \Children{ unable to keep God's law.}

\Quote{Romans 5:12\index[rom]{05:12@5:12}}{Therefore, just as sin entered the world through one man, and death through sin, and in this way death came to all people, because all sinned.}

\subsection{Q 15. Since no one can keep the law, what is its purpose?}
\Children{That we may know the holy nature }and will \Children{of God, and the sinful nature }and disobedience \Children{of our hearts; and thus our need of a Savior.} The law also teaches and exhorts us to live a life worthy of our Savior.

\Quote{Romans 3:20\index[rom]{03:20@3:20}}{No one will be declared righteous in God's sight by the works of the law; rather, through the law we become conscious of our sin.}

\subsection{Q 16. What is sin?}
\Children{Sin is rejecting or ignoring God in the world he created, }rebelling against him by living without reference to him, \Children{not being or doing what he requires in his law}\thinspace{}---\thinspace{}resulting in our death and the disintegration of all creation\Children{.}

\Quote{1 John 3:4\index[1jo]{3:4}}{Everyone who sins breaks the law; in fact, sin is lawlessness.}

\subsection{Q 17. What is idolatry?}
\Children{Idolatry is trusting in created things rather than the Creator} for our hope and happiness, significance and security\Children{.}

\Quote{Romans 1:21\index[rom]{01:21@1:21} and 25\index[rom]{01:25@1:25}}{For although they knew God, they neither glorified him as God nor gave thanks to him, but their thinking became futile and their foolish hearts were darkened\,\dots{}\,They exchanged the truth about God for a lie, and worshiped and served created things rather than the Creator.}

\subsection{Q 18. Will God allow our disobedience and idolatry to go unpunished?}
\Children{No, }every sin is against the sovereignty, holiness, and goodness of God, and against his righteous law, and \Children{God is righteously angry with our sins and will punish them }in his just judgment \Children{both in this life, and in the life to come.}

\Quote{Ephesians 5:5--6\index[eph]{5:5--6}}{For of this you can be sure: No immoral, impure or greedy person\thinspace{}---\thinspace{}such a person is an idolater\thinspace{}---\thinspace{}has any inheritance in the kingdom of Christ and of God. Let no one deceive you with empty words, for because of such things God's wrath comes on those who are disobedient.}

\subsection{Q 19. Is there any way to escape punishment and be brought back into God's favor?}
\Children{Yes, }to satisfy his justice, \Children{God} himself, out of mere mercy, \Children{reconciles us to himself }and delivers us from sin and from the punishment for sin, \Children{by a Redeemer.}

\Quote{Isaiah 53:10--11\index[isa]{53:10--11}}{Yet it was the \textsc{Lord's} will to crush him and cause him to suffer, and though the \textsc{Lord} makes his life an offering for sin, he will see his offspring and prolong his days, and the will of the \textsc{Lord} will prosper in his hand. After he has suffered, he will see the light of life and be satisfied; by his knowledge my righteous servant will justify many, and he will bear their iniquities.}

\subsection[Q 20. Who is the Redeemer?]{Q 20. Who is the Redeemer?}
\Children{The only Redeemer is the Lord Jesus Christ}, the eternal Son of God, in whom God became man and bore the penalty for sin himself\Children{.}

\Quote{1 Timothy 2:5\index[1ti]{2:5}}{For there is one God and one mediator between God and mankind, the man Christ Jesus.}

\end{document}