% !TeX root = 00-main.tex


\section{Part 2. Christ, Redemption, Grace}

\subsection{Q 21. What sort of Redeemer is needed to bring us back to God?}
\Children{One who is truly human and also truly God.}

\Quote{Isaiah 9:6\index[isa]{09:6@9:6}}{For to us a child is born, to us a son is given, and the government will be on his shoulders. And he will be called Wonderful Counselor, Mighty God, Everlasting Father, Prince of Peace.}

\subsection{Q 22. Why must the Redeemer be truly human?}
\Children{That in human nature he might on our behalf perfectly obey the whole law and suffer the punishment for human sin}; and also that he might sympathize with our weaknesses\Children{.}

\Quote{Hebrews 2:17\index[heb]{2:17}}{For this reason he had to be made like them, fully human in every way, in order that he might become a merciful and faithful high priest in service to God, and that he might make atonement for the sins of the people.}

\subsection{Q 23. Why must the Redeemer be truly God?}
\Children{That because of his divine nature his obedience and suffering would be perfect and effective}; and also that he would be able to bear the righteous anger of God against sin and yet overcome death\Children{.}

\Quote{Acts 2:24\index[act]{02:24@2:24}}{But God raised him from the dead, freeing him from the agony of death, because it was impossible for death to keep its hold of him.}

\subsection{Q 24. Why was it necessary for Christ, the Redeemer, to die?}
Since death is the punishment for sin, \Children{Christ died willingly in our place to deliver us from the power and penalty of sin and bring us back to God.} By his substitutionary atoning death, he alone redeems us from hell and gains for us forgiveness of sin, righteousness, and everlasting life.

\Quote{Colossians 1:21--22\index[col]{1:21--22}}{\sloppy Once you were alienated from God and were enemies in your minds because of your evil behavior. But now he has reconciled you by Christ's physical body through death to present you holy in his sight, without blemish and free from accusation.}

\subsection{Q 25. Does Christ's death mean all our sins can be forgiven?}
\Children{Yes, because Christ's death on the cross fully paid the penalty for our sin, God} graciously imputes Christ's righteousness to us as if it were our own and \Children{will remember our sins no more.}

\Quote{2 Corinthians 5:21\index[2co]{5:21}}{God made him who had no sin to be sin for us, so that in him we might become the righteousness of God.}

\subsection{Q 26. What else does Christ's death redeem?}
Christ's death is the beginning of the redemption and renewal of \Children{every part of fallen creation}, as he powerfully directs all things for his own glory and creation's good\Children{.}

\Quote{Colossians 1:19--20\index[col]{1:19--20}}{For God was pleased to have all his fullness dwell in him, and through him to reconcile to himself all things, whether things on earth or things in heaven, by making peace through his blood, shed on the cross.}

\subsection{Q 27. Are all people, just as they were lost through Adam, saved through Christ?}
\Children{No, only those who are elected\footnote{Editor's note: see also Q 32.} by God and united to Christ by faith.} Nevertheless God in his mercy demonstrates common grace even to those who are not elect, by restraining the effects of sin and enabling works of culture for human well-being.

\Quote{Romans 5:17\index[rom]{05:17@5:17}}{For if, by the trespass of the one man, death reigned through that one man, how much more will those who receive God's abundant provision of grace and of the gift of righteousness reign in life through the one man, Jesus Christ!}

\subsection{Q 28. What happens after death to those not united to Christ by faith?}
At the day of judgment they will receive the fearful but just sentence of condemnation pronounced against them. \Children{They will be cast out from the} favorable \Children{presence of God, into hell, to be justly} and grievously \Children{punished, forever.}

\Quote{John 3:16--18\index[joh]{03:16--18@3:16--18} and 36\index[joh]{03:36@3:36}}{For God so loved the world that he gave his one and only Son, that whoever believes in him shall not perish but have eternal life. For God did not send his Son into the world to condemn the world, but to save the world through him. Whoever believes in him is not condemned, but whoever does not believe stands condemned already because they have not believed in the name of God's one and only Son\,\dots{}\,Whoever believes in the Son has eternal life, but whoever rejects the Son will not see life, for God's wrath remains on them.}

\subsection{Q 29. How can we be saved?}
\Children{Only by faith in Jesus Christ and in his substitutionary atoning death on the cross}; so even though we are guilty of having disobeyed God and are still inclined to all evil, nevertheless, God, without any merit of our own but only by pure grace, imputes to us the perfect righteousness of Christ when we repent and believe in him\Children{.}

\Quote{Ephesians 2:8--9\index[eph]{2:8--9}}{For it is by grace you have been saved, through faith\thinspace{}---\thinspace{}and this is not from yourselves, it is the gift of God\thinspace{}---\thinspace{}not by works, so that no one can boast.}

\subsection{Q 30. What is faith in Jesus Christ?}
Faith in Jesus Christ is acknowledging the truth of everything that God has revealed in his Word, trusting in him, and also \Children{receiving and resting on him alone for salvation as he is offered to us in the gospel.}

\Quote{Galatians 2:20\index[gal]{2:20}}{I have been crucified with Christ and I no longer live, but Christ lives in me. The life I now live in the body, I live by faith in the Son of God, who loved me and gave himself for me.}

\subsection{Q 31. What do we believe by true faith?}
Everything taught to us in the gospel. The Apostles' Creed expresses what we believe in these words: \Children{We believe in God the Father Almighty, Maker of heaven and earth; and in Jesus Christ his only Son our Lord, who was conceived by the Holy Spirit, born of the virgin Mary, suffered under Pontius Pilate, was crucified, died, and was buried. He descended into hell. The third day he rose again from the dead. He ascended into heaven, and is seated at the right hand of God the Father Almighty; from there he will come to judge the living and the dead. We believe in the Holy Spirit, the holy catholic church, the communion of saints, the forgiveness of sins, the resurrection of the body, and the life everlasting.}

\Quote{Jude 1:3\index[jud]{1:3}}{I\,\dots{}\,urge you to contend for the faith that was once for all entrusted to God's holy people.}

\subsection{Q 32. What do justification and sanctification mean?}
\Children{Justification means our declared righteousness before God}, made possible by Christ's death and resurrection for us\Children{.} \Children{Sanctification means our gradual, growing righteousness}, made possible by the Spirit's work in us\Children{.}

\Quote{1 Peter 1:1--2\index[1pe]{1:1--2}}{To God's elect\,\dots{}\,who have been chosen according to the foreknowledge of God the Father, through the sanctifying work of the Spirit, to be obedient to Jesus Christ and sprinkled with his blood: Grace and peace be yours in abundance.}

\subsection{Q 33. Should those who have faith in Christ seek their salvation through their own works, or anywhere else?}
\Children{No, }they should not, \Children{as everything necessary to salvation is found in Christ.} To seek salvation through good works is a denial that Christ is the only Redeemer and Savior.

\Quote{Galatians 2:16\index[gal]{2:16}}{Know that a person is not justified by the works of the law, but by faith in Jesus Christ. So we, too, have put our faith in Christ Jesus that we may be justified by faith in Christ and not by the works of the law, because by the works of the law no one will be justified.}

\subsection{Q 34. Since we are redeemed by grace alone, through Christ alone, must we still do good works and obey God's Word?}
\Children{Yes, }because Christ, having redeemed us by his blood, also renews us by his Spirit; \Children{so that our lives may show love and gratitude to God; }so that we may be assured of our faith by the fruits; \Children{and so that by our godly behavior others may be won to Christ.}

\Quote{1 Peter 2:9--12\index[1pe]{2:9--12}}{But you are a chosen people, a royal priesthood, a holy nation, God's special possession, that you may declare the praises of him who called you out of darkness into his wonderful light. Once you were not a people, but now you are the people of God; once you had not received mercy, but now you have received mercy. Dear friends, I urge you, as foreigners and exiles, to abstain from sinful desires, which wage war against your soul. Live such good lives among the pagans that, though they accuse you of doing wrong, they may see your good deeds and glorify God on the day he visits us.}

\subsection{Q 35. Since we are redeemed by grace alone, through faith alone, where does this faith come from?}
All the gifts we receive \Children{from} Christ we receive through \Children{the Holy Spirit}, including faith itself\Children{.}

\Quote{Titus 3:4--6\index[tit]{3:4--6}}{But when the kindness and love of God our Savior appeared, he saved us, not because of righteous things we had done, but because of his mercy. He saved us through the washing of rebirth and renewal by the Holy Spirit, whom he poured out on us generously through Jesus Christ our Savior.}

