% !TeX root = 00-main.tex

\section[Part 3. Spirit, Restoration, Growing In Grace][Spirit, Restoration, Growing In Grace]{Part 3. Spirit, Restoration, Growing In Grace}

\subsection{Q 36. What do we believe about the Holy Spirit?}
\Children{That he is God, coeternal with the Father and the Son}, and that God grants him irrevocably to all who believe\Children{.}

\Quote{John 14:16--17\index[joh]{14:16--17}}{I will ask the Father, and he will give you another advocate to help you and be with you forever\thinspace{}---\thinspace{}the Spirit of truth. The world cannot accept him, because it neither sees him nor knows him. But you know him, for he lives with you and will be in you.}

\subsection{Q 37. How does the Holy Spirit help us?}
\Children{The Holy Spirit convicts us of our sin}, comforts us, guides us, gives us spiritual gifts and the desire to obey God; \Children{and he enables us to pray and to understand God's Word.}

\Quote{Ephesians 6:17--18\index[eph]{6:17--18}}{Take the helmet of salvation and the sword of the Spirit, which is the word of God. And pray in the Spirit on all occasions with all kinds of prayers and requests.}

\subsection{Q 38. What is prayer?}
\Children{Prayer is pouring out our hearts to God} in praise, petition, confession of sin, and thanksgiving\Children{.}

\Quote{Psalm 62:8\index[psa]{62:8}}{Trust in him at all times, you people; pour out your hearts to him, for God is our refuge.}

\subsection{Q 39. With what attitude should we pray?}
\Children{With love, perseverance, and gratefulness}; in humble submission to God's will, knowing that, for the sake of Christ, he always hears our prayers\Children{.}

\Quote{Philippians 4:6\index[phi]{4:6}}{Do not be anxious about anything, but in every situation, by prayer and petition, with thanksgiving, present your requests to God.}

\subsection{Q 40. What should we pray?}
\Children{The whole Word of God directs }and inspires \Children{us in what we should pray}, including the prayer Jesus himself taught us\Children{.}

\Quote{Ephesians 3:14--21\index[eph]{3:14--21}}{For this reason I kneel before the Father, from whom every family in heaven and on earth derives its name. I pray that out of his glorious riches he may strengthen you with power through his Spirit in your inner being, so that Christ may dwell in your hearts through faith. And I pray that you, being rooted and established in love, may have power, together with all the Lord's holy people, to grasp how wide and long and high and deep is the love of Christ, and to know this love that surpasses knowledge\thinspace{}---\thinspace{}that you may be filled to the measure of all the fullness of God. Now to him who is able to do immeasurably more than all we ask or imagine, according to his power that is at work within us, to him be glory in the church and in Christ Jesus throughout all generations, for ever and ever! Amen.}

\subsection{Q 41. What is the Lord's Prayer?}
\Children{Our Father in heaven, hallowed\footnote{Editor's note: or ``holy''.} be your name, your kingdom come, your will be done, on earth as it is in heaven. Give us today our daily bread. And forgive us our debts, as we also have forgiven our debtors. And lead us not into temptation, but deliver us from evil.}

\Quote{Matthew 6:9\index[mat]{06:9@6:9}}{This, then, is how you should pray: ``Our Father in heaven, hallowed be your name {\dots}''}

\subsection{Q 42. How is the Word of God to be read and heard?}
\Children{With diligence, preparation, and prayer; so that we may accept it with faith}, store it in our hearts,\Children{\ and practice it in our lives.}

\Quote{2 Timothy 3:16--17\index[2ti]{3:16--17}}{All Scripture is God-breathed and is useful for teaching, rebuking, correcting and training in righteousness, so that the servant of God may be thoroughly equipped for every good work.}

\subsection{Q 43. What are the sacraments or ordinances?}
The sacraments or ordinances given by God and instituted by Christ, namely \Children{baptism and the Lord's Supper}, are visible signs and seals that we are bound together as a community of faith by his death and resurrection\Children{.} By our use of them the Holy Spirit more fully declares and seals the promises of the gospel to us.

\Quote{Romans 6:4\index[rom]{06:4@6:4}}{We were therefore buried with him through baptism into death in order that, just as Christ was raised from the dead through the glory of the Father, we too may live a new life.}

\Quote{Luke 22:19--20\index[luk]{22:19--20}}{And he took bread, gave thanks and broke it, and gave it to them, saying, ``This is my body given for you; do this in remembrance of me.'' In the same way, after the supper he took the cup, saying, ``This cup is the new covenant in my blood, which is poured out for you.''}

\subsection{Q 44. What is baptism?}
\Children{Baptism is the washing with water in the name of the Father, the Son, and the Holy Spirit}; it signifies and seals our adoption into Christ, our cleansing from sin, and our commitment to belong to the Lord and to his church\Children{.}

\Quote{Matthew 28:19\index[mat]{28:19}}{Therefore go and make disciples of all nations, baptizing them in the name of the Father and of the Son and of the Holy Spirit.}

\subsection{Q 45. Is baptism with water the washing away of sin itself?}
\Children{No, only the blood of Christ }and the renewal of the Holy Spirit \Children{can cleanse us from sin.}

\Quote{Luke 3:16\index[luk]{03:16@3:16}}{John answered them all, ``I baptize you with water. But one who is more powerful than I will come, the straps of whose sandals I am not worthy to untie. He will baptize you with the Holy Spirit and fire.''}

\subsection{Q 46. What is the Lord's Supper?}
\Children{Christ commanded all Christians to eat bread and to drink from the cup in thankful remembrance of him} and his death\Children{.} The Lord's Supper is a celebration of the presence of God in our midst; bringing us into communion with God and with one another; feeding and nourishing our souls. It also anticipates the day when we will eat and drink with Christ in his Father's kingdom.

\Quote{1 Corinthians 11:23--26\index[1co]{11:23--26}}{The Lord Jesus, on the night he was betrayed, took bread, and when he had given thanks, he broke it and said, ``This is my body, which is for you; do this in remembrance of me.'' In the same way, after supper he took the cup, saying, ``This cup is the new covenant in my blood; do this, whenever you drink it, in remembrance of me.'' For whenever you eat this bread and drink this cup, you proclaim the Lord's death until he comes.}

\subsection{Q 47. Does the Lord's Supper add anything to Christ's atoning work?}
\Children{No, Christ died once for all.} The Lord's Supper is a covenant meal celebrating Christ's atoning work; as it is also a means of strengthening our faith as we look to him, and a foretaste of the future feast. But those who take part with unrepentant hearts eat and drink judgment on themselves.

\Quote{1 Peter 3:18\index[1pe]{3:18}}{For Christ died for sins once for all, the righteous for the unrighteous, to bring you to God.}

\subsection{Q 48. What is the church?}
God chooses and preserves for himself \Children{a community elect\-ed for eternal life and united by faith, who love, follow, learn from, and worship God together.} God sends out this community to proclaim the gospel and prefigure Christ's kingdom by the quality of their life together and their love for one another.

\Quote{2 Thessalonians 2:13\index[2th]{2:13}}{But we ought always to thank God for you, brothers and sisters loved by the Lord, because God chose you as first-fruits to be saved through the sanctifying work of the Spirit and through belief in the truth.}

\subsection{Q 49. Where is Christ now?}
\Children{Christ rose bodily from the grave on the third day after his death and is seated at the right hand of the Father}, ruling his kingdom and interceding for us, until he returns to judge and renew the whole world\Children{.}

\Quote{Ephesians 1:19--21\index[eph]{1:19--21}}{That power is the same as the mighty strength he exerted when he raised Christ from the dead and seated him at his right hand in the heavenly realms, far above all rule and authority, power and dominion, and every name that is invoked, not only in the present age but also in the one to come.}

\subsection{Q 50. What does Christ's resurrection mean for us?}
\Children{Christ triumphed over sin and death} by being physically resurrected\Children{, so that all who trust in him are raised to new life in this world and to everlasting life in the world to come.} Just as we will one day be resurrected, so this world will one day be restored. But those who do not trust in Christ will be raised to everlasting death.

\Quote{1 Thessalonians 4:13--14\index[1th]{4:13--14}}{Brothers and sisters, we do not want you to be uninformed about those who sleep in death, so that you do not grieve like the rest of mankind, who have no hope. For we believe that Jesus died and rose again, and so we believe that God will bring with Jesus those who have fallen asleep in him.}

\subsection{Q 51. Of what advantage to us is Christ's ascension?}
\Children{Christ }physically ascended on our behalf, just as he came down to earth physically on our account, and he \Children{is now advocating for us in the presence of his Father}, preparing a place for us,\Children{\ and also sends us his Spirit.}

\Quote{Romans 8:34\index[rom]{08:34@8:34}}{Christ Jesus who died\thinspace{}---\thinspace{}more than that, who was raised to life\thinspace{}---\thinspace{}is at the right hand of God and is also interceding for us.}

\subsection{Q 52. What hope does everlasting life hold for us?}
It reminds us \Children{that }this present fallen world is not all there is; soon \Children{we will live with and enjoy God forever }in the new city, \Children{in the new heaven and the new earth, where we will be }fully and \Children{forever freed from all sin }and will inhabit renewed, resurrection bodies \Children{in a renewed, restored creation.}

\Quote{Revelation 21:1--4\index[rev]{21:1--4}}{Then I saw a new heaven and a new earth, for the first heaven and the first earth had passed away, and there was no longer any sea. I saw the Holy City, the new Jerusalem, coming down out of heaven from God, prepared as a bride beautifully dressed for her husband. And I heard a loud voice from the throne saying, ``Look! God's dwelling place is now among the people, and he will dwell with them. They will be his people, and God himself will be with them and be their God. He will wipe every tear from their eyes. There will be no more death or mourning or crying or pain, for the old order of things has passed away.''}

